---
title: "stm testing"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

# read the document
```{r}
PAJournals<-read.csv("/home/bobking1224/R/CSS/Local gov STM/dataNewMerged.csv", stringsAsFactors = FALSE)
```

```{r}
library(stm)
```

```{r}
processed <- textProcessor(PAJournals$documents, metadata = PAJournals, removestopwords = TRUE, customstopwords = c("local government"))
```

# Prepare the document
```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```
```{r}
docs <- out$documents
vocab <- out$vocab
meta <-out$meta
```

```{r}
First_STM <- stm(documents = out$documents, vocab = out$vocab,
              K = 25, 
              max.em.its = 75, data = out$meta,
              init.type = "Spectral", verbose = FALSE)
```

```{r}
plot(First_STM)
```

```{r}
labelTopics(First_STM)
```

```{r}
thoughts3 <- findThoughts(First_STM, texts = meta$documents, n = 4, 
                           topics = 25)$docs[[1]]

idx1 <- match(thoughts3[1],meta$documents)
title1 <- meta$Title[idx1]
title1

idx2 <- match(thoughts3[2],meta$documents)
title2 <- meta$Title[idx2]
title2

idx3 <- match(thoughts3[3],meta$documents)
title3 <- meta$Title[idx3]
title3

idx4 <- match(thoughts3[4],meta$documents)
title4 <- meta$Title[idx4]
title4
```

```{r}
First_STM <- stm(documents = out$documents, vocab = out$vocab,
              K = 26, 
              max.em.its = 75, data = out$meta,
              init.type = "Spectral", verbose = FALSE)
```

```{r}
plot(First_STM)
```

```{r}
labelTopics(First_STM)
```

```{r}
First_STM <- stm(documents = out$documents, vocab = out$vocab,
              K = 27, 
              max.em.its = 75, data = out$meta,
              init.type = "Spectral", verbose = FALSE)
```

```{r}
plot(First_STM)
```

```{r}
labelTopics(First_STM)
```

```{r}
First_STM <- stm(documents = out$documents, vocab = out$vocab,
              K = 28, 
              max.em.its = 75, data = out$meta,
              init.type = "Spectral", verbose = FALSE)
```

```{r}
plot(First_STM)
```

```{r}
labelTopics(First_STM)
```

```{r}
First_STM <- stm(documents = out$documents, vocab = out$vocab,
              K = 29, 
              max.em.its = 75, data = out$meta,
              init.type = "Spectral", verbose = FALSE)
```

```{r}
plot(First_STM)
```

```{r}
labelTopics(First_STM)
```


# show the most relevant text
```{r}

findThoughts(First_STM, texts = meta$documents,
     n = 2, topics = 3)
```

```{r}
findingk <- searchK(out$documents, out$vocab, K = c(10:30), data = meta, verbose=FALSE)

plot(findingk)
```
     
The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
plot(findingk)
```

